\include{header/header}
\include{header/glossary_settings}
\include{header/title_macros}

\addbibresource{misc/literature.bib}

\begin{document}
\include{misc/abbreviations}
%\include{misc/glossary}

% Replace by useful values!
\makeTheTitlepage{
    organization={FH Aachen},
    title={Unsupervised Pre-Training for Vietnamese \\ Automatic Speech Recognition in the HYKIST Project},
    type={Bachelorarbeit},
    faculty={Fachbereich Medizintechnik und Technomathematik},
    department={Bachelorstudiengang Biomedizinische Technik},
    author={Le Duc Khai},
    matrikel={Matrikelnummer: 3089345},
    place=Jülich,
    date=\today,
    examiner={Prof. Dr. rer. nat. Ilya E. Digel, FH Aachen},
    secondExaminer={Christoph M. Lüscher M.Sc., RWTH Aachen},
    advisorFirst={Sen. Prof. Dr.-Ing. Hermann Ney, RWTH Aachen},
    advisorSecond={PD Dr. rer. nat. Ralf Schlüter, RWTH Aachen},
}

%\includepdf[pages={1}]{docs/ba_faber_punctuation}

\clearpage

\include{chapter/Erklaerung}

\tableofcontents

\begin{spacing}{1.2}
    %\include{chapter/introduction}
    %\include{chapter/demo_chapter}

    \include{chapter/Abstract}
    
    \include{chapter/Introduction_01}
    \include{chapter/Introduction_02}
    \include{chapter/Introduction_03}
    
    \include{chapter/Theory_01}
    \include{chapter/Theory_02}
    \include{chapter/Theory_03}
    
    \include{chapter/Experiments_01}
    \include{chapter/Experiments_02}
    \include{chapter/Experiments_03}
    
    \include{chapter/Experimental_results_01}
    \include{chapter/Experimental_results_02}
    %\include{chapter/Experimental_results_03}
    \include{chapter/Experimental_results_04}
    \include{chapter/Experimental_results_05}
    \include{chapter/Experimental_results_06}
    \include{chapter/Experimental_results_07}
    
    \include{chapter/Conclusion}
    
    \appendix
    %\include{chapter/appendix}

    \printbibliography[heading=bibnumbered,
    title={Bibliography}]

    %\include{misc/symbols}
    \glsaddall[types={symbolslist,glossaryx}]

    % This command would add *all** non-mentioned glossary entries (e.g. the acronyms)
    % \glsaddall
    % It's better to mention those in the text via 
    % \acrlong{BMS}, \acrshort{BMS}, and \acrfull{BMS}.
    % Because then the page numbers occur correctly in the list of acronyms
    \clearpage

    %\printglossary[type=symbolslist,style=symbunitlong,title=List of Symbols]
    \printglossary[type=acronym, title=List of Abbreviations and Glossaries]

    %\printglossary[type=glossaryx,style=glossaryxstyle,title=Glossary]
    %\printglossary[type=glossaryx, title=Glossary]
   
    \listoffigures
    \listoftables
    
\end{spacing}

\end{document}

